% Created 2015-06-07 Sun 08:23
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\author{piepsilon}
\date{\today}
\title{db}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\tableofcontents

\section{Database}
\label{sec-1}
\subsection{Expert Oracle Database Architecture}
\label{sec-1-1}
\subsubsection{Architecture Overview}
\label{sec-1-1-1}
\begin{enumerate}
\item Database and Instance
\label{sec-1-1-1-1}
\begin{enumerate}
\item Database
\label{sec-1-1-1-1-1}
A collection of physical operating system files or disks. When using Oracle
Automatic Storage Management (ASM) or RAW partitions, the database may not
appear as individual, separate files in the operating system, but the 
definition remains the same.
\begin{enumerate}
\item A single tenant database
\end{enumerate}
This is a self-contained set of data files, control files, redo log files,
 parameter files, and so on, that include all of the Oracle metadata 
(the definition of ALL$_{\text{OBJECTS}}$, for example), Oracle data, and Oracle code 
(such as the code for DBMS$_{\text{OUTPUT}}$), in addition to all of the application 
metadata, data, and code. This is the only type of database in releases prior 
to version 12c.
\begin{enumerate}
\item A container or root database
\end{enumerate}
This is a self-contained set of data files, control files, redo log files, 
parameter files, and so on, that only include the Oracle metadata, Oracle data,
 and Oracle code. There are no application objects or code in these data 
files—only Oracle-supplied metadata and Oracle-supplied code objects. This 
database is self-contained in that it can be mounted and opened without any 
other supporting physical structures.
\begin{enumerate}
\item A pluggable database
\end{enumerate}
This is a set of data files only. It is not self-contained. A pluggable 
database needs a container database to be “plugged into” to be opened and 
accessible. These data files contain only metadata for application objects, 
application data, and code for those applications. There is no Oracle metadata
 or any Oracle code in these data files. There are no redo log files, control
 files, parameter files, and so on—only data files associated with a pluggable 
database. The pluggable database inherits these other types of files from the 
container database it is currently plugged into.
\item Instance
\label{sec-1-1-1-1-2}
An instance is simply a set of operating system processes, or a single process
 with many threads, and some memory.
\item relationship of database and instance
\label{sec-1-1-1-1-3}
\begin{enumerate}
\item a single tenant database and container database may be mounted and opened by
many instances
\item single tenant database and container database can only have one instance
\end{enumerate}
working on it.
\begin{enumerate}
\item one instance can work on many pluggable database
\item ORAC allow one tenant database or container database to be managed by many
\end{enumerate}
instances
\begin{enumerate}
\item one instance can only mount and open one tenant or container database at any
\end{enumerate}
point, and it's safe to say an instance will mount and open, at most, a single
database in its entire lifetime.
\end{enumerate}
\end{enumerate}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}